---
title: "Tutorial 6: Refactoring R Code"
bibliography: references.bib
---

# Introduction

In this tutorial, you will refactor the code into separate scripts corresponding to each section. The dataset we will use comes from the `palmerpenguins` package, which contains measurements of penguins from three species.

The R programming language [@R]  and the following R packages were used to perform the analysis:  knitr [@knitr], tidyverse [@tidyverse], and Quarto [@Allaire_Quarto_2022]. 

## Load Libraries and Data

```{r load}
#| echo: false
#| tbl-cap: Load libraries and data.

data <- readr::read_csv("~/work/data/raw/penguins.csv")
knitr::kable(head(data))
```

# Methods

In this section, we perform exploratory data analysis (EDA) and prepare the data for modeling.

```{r glimpse}
#| echo: false
#| tbl-cap: Glimpse at data.

# Summary statistics
dplyr::glimpse(data)
```

```{r summary}
#| echo: false
#| tbl-cap: Summarise data.

# Summary statistics
summary <- readr::read_csv("~/work/output/summary.csv")
knitr::kable(data)
```

```{r clean}
#| echo: false
#| tbl-cap: Prepare data for modelling.

# Prepare data for modeling
data <- readr::read_csv("~/work/data/processed/penguins_cleaned.csv")
knitr::kable(head(data))
```

# Model

We will fit a classification model using `tidymodels` to predict the species of a penguin based on its physical characteristics.

```{r fit}
#| echo: false
#| tbl-cap: Fit classification model.

# Fit model
penguin_fit <- readr::read_rds("~/work/output/penguin_fit.rds")
knitr::kable(summary(data))
```

# Results

We evaluate the performance of the model using the test dataset.

```{r result}
#| echo: false
#| tbl-cap: Model results.

conf_mat <- readr::read_rds("~/work/output/conf_mat.rds")
knitr::kable(conf_mat$table)
```

## Libraries Run

Test the usage of packages in the report.

```{r pack}
#| echo: false
#| tbl-cap: Test the usage of packages in the report.

func_outputs <- readr::read_csv("~/work/output/summary.csv")
knitr::kable(func_outputs)
```

# Conclusion

In this tutorial, we:

- Loaded and cleaned the `palmerpenguins` dataset.
- Performed exploratory data analysis.
- Built a k-Nearest Neighbors classification model using `tidymodels`.
- Evaluated the model's performance.

# References